Which ITG Stepcharts are Turniest?

### 2019-03-16 itg/3/paper.tex
more edits

As before, the code is available at \url{https://github.com/bblum/sigbovik/blob/master/itg/code/ITG.hs}.
To give an idea of how much its elegance has been despoiled % hi william
since the last version:
98 lines of Haskell (which computed crossovers, footswitches, jacks, doubleswitches, \textit{and} crossover footswitches)
has grown to 248 lines (just to handle this one new feature),
and the once-simple datatype definition of

@@

I put this section here only just so I could have something to forward-reference back in \Cref{sec:analyzing}.
I always wanted to do that, you know?
% TODO: put a pict anyway? if you find one

@@

It would be cool to integrate this (and the preceding two algorithms \cite{turniness,crossoveriness})
into
%Simply Love \cite{simplylove}, or whatever
the community's prevailing stepmania theme.
%may be in the future.
Currently, as shown in \Cref{fig:songpreview}(a),
the song preview screen wastes considerable space displaying the count of more irrelevant chart aspects
such as mines (now used primarily for signaling the presence of footswitches)
and hands (now mostly stepped with the feet by bracketing anyways).
I bet the community might actually pay attention to my work---the holy grail of research, honestly---if
the premier dance game theme showed precisely how technical a chart was, as in (b).

>>>>

As before, the code is available at \url{https://github.com/bblum/sigbovik/blob/master/itg/code/ITG.hs}.
To give an idea of how much its elegance has been despoiled % hi william
since the last version:
98 lines of Haskell (which computed crossovers, footswitches, jacks, doubleswitches, \textit{and} crossover footswitches)
has grown to 248 lines (just to handle this one. new. feature),
and the once-simple datatype definition of

@@

I put this section here only just so I could have something to forward-reference back in \Cref{sec:analyzing}.
I always wanted to do that, you know?
I mean, footswitch brackets are also a real thing, but still. $\bar{~~}$\textbackslash\_(ツ)\_/$\bar{~~}$
% not-to-to: put a pict anyway? if you find one
% actually, joke comes off better w/o

@@

It would be cool to integrate this (and the preceding two algorithms \cite{turniness,crossoveriness})
into
%Simply Love \cite{simplylove}, or whatever
the community's prevailing stepmania theme.
%may be in the future.
Currently, as shown in \Cref{fig:songpreview}(a),
the song preview screen wastes considerable space displaying the count of irrelevant chart aspects
such as mines (now used primarily for signaling the presence of footswitches)
and hands (now mostly stepped with the feet by bracketing anyways).
I bet the community might actually pay attention to my work---the holy grail of research, honestly---if
popular themes used it to show precisely how technical a chart was, as in (b).
